Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-11-30 Manuscript/manuscript.tex

The lack of electronic polarizability has been a concern since the
early days of classical MD simulations of lipids \cite{jonsson86,egberts94, berendsen1996},
where the atomic charges were scaled by a factor of 1/2 to effectively
include the electrostatic screening from the missing electronic polarizability.
The electronic continuum correction (ECC) is a more sophisticated version of the charge scaling.
In ECC, the charges are rescaled with a pre-determined scaling factor, $f_q$,
\begin{equation}
  f_q = \frac{1}{\sqrt{\epsilon_{el}}} ,
\end{equation}
where $\epsilon_{el}$ is the high-frequency dielectric constant of electrons.
The value of $\epsilon_{el} = 1.78$ for water solutions gives the scaling
factor of $f_q \approx 0.75$ for aquaeous environments \cite{leontyev09}.
This has been recently applied to improve classical models for ions and
other biomolecules \cite{Pluharova2014, martinek17, melcr18}
\todo{Pavel can probably update this}.

@@

%Compared to POPS, POPC is a zwitterionic neutral molecule with a zero total charge; 
%scaling it by any factor does not affect it. 
%Partial charges of the atoms in POPC are not physical observables, 
%and vary greatly between different models. \cite{botan15, catte16, nmrlipids_proj4, Pluhackova2016}
%The choice of a larger scaling factor in ECC-POPC represents the fact that 
%the set of partial charges in the initial model for ECC-POPC, the Lipid14 model \cite{dickson14}, 
%was determined in the beginning as less polar compared to other models.

@@

%It is important to note that the value of the high frequency dielectric constant  
%is around 2 for almost any biologically relevant environment \citep{leontyev11}. 
%This means that even interfaces like biological membranes do not contain discontinuities of the electronic continuum. 
%The dielectric discontinuity in a lipid bilayer thus arises only 
%from the orientational polarization of the molecules, which is accounted for explicitly in standard MD simulations.  
%Therefore, the same correction for the electronic polarizability can be  
%applied throughout the lipid bilayer/aqueous solution interface.

@@

To validate the structures of lipid bilayers, the scattering form factors and C-H bond order parameters
were calculated and compared against the experimental data as described previously~\cite{botan15,ollila16,melcr18,nmrlipids_proj4}.
%in simulations without ions were validated against NMR 
%by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating 
%as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
%The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
%while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
%(see next section and Fig.~\ref{simVSexpNOions_POPS}). 
The order parameters for each C-H bond of individual lipids in the trajectory were first averaged
over the time. Then the average over lipids was taken and the standard error of the mean of this
average was used as an error bar \cite{botan15,ollila16,nmrlipids_proj4}.

@@

>>>>

The lack of electronic polarizability has been a concern since the
early days of classical MD simulations of lipids \cite{jonsson86,egberts94, berendsen1996},
where the atomic charges were scaled by a factor of 1/2 to effectively
include the electrostatic screening from the missing electronic polarizability.
The electronic continuum correction (ECC) is a more sophisticated version of the charge scaling.

The polarization of electrons in ECC-lipids uses the implicit method termed electronic continuum correction (ECC). \cite{leontyev09, Pluharova2014, martinek17, melcr18} 
In this method, a system of polarizable particles is represented with an equivalent system of particles with fixed charges. 
This is practically achieved rescaling the charges with a pre-determined scaling factor, $f_q$,
which is derived from the high-frequency dielectric constant of electrons, $\epsilon_{el}$, as
-OR-
In ECC, the charges are rescaled with a pre-determined scaling factor, $f_q$,
\begin{equation}
  f_q = \frac{1}{\sqrt{\epsilon_{el}}} ,
\end{equation}
where $\epsilon_{el}$ is the high-frequency dielectric constant of electrons.
The value of $\epsilon_{el} = 1.78$ for water solutions gives the scaling
factor of $f_q \approx 0.75$ for aquaeous environments \cite{leontyev09}.
This has been recently applied to improve classical models for ions and
other biomolecules \cite{Pluharova2014, martinek17, melcr18}
\todo{Pavel can probably update this}.

@@

@@

@@

To validate the structures of lipid bilayers, the scattering form factors and C-H bond order parameters
were calculated and compared against the experimental data as described previously~\cite{botan15,ollila16,melcr18,nmrlipids_proj4}.
%in simulations without ions were validated against NMR 
%by calculating the order parameters for the C-H bonds and against \mbox{X-ray} scattering experiments by evaluating 
%as was done in Refs.~\citenum{catte16, melcr18, nmrlipids_proj4}.
%NMR order parameters validate the structures sampled by the individual lipid molecules with atomic resolution. 
%The simulated order parameters were calculated for all C-H bonds in lipid molecules, 
%while all order paremeters in the head group and only some in the \ce{C-H} groups in tails were resolved experimentally
%(see next section and Fig.~\ref{simVSexpNOions_POPS}). 
The order parameters for each C-H bond of individual lipids in the trajectory were first averaged
over the time. Then the average over lipids was taken and the standard error of the mean of this
average was used as an error bar \cite{botan15,,ollila16,nmrlipids_proj4}.

@@

The simulation parameters used in this work are summarized in Table~\ref{tbl:mdpar}.
